---
title: "Lab2_Akhila"
author: "Akhila"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#PART A

##Run the code below to load the following data set.
```{r}

file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)

```

##Recode season to wave with the following code
```{r}

library(tidyverse)

benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))

```

##1. Fit a model of the form lm(math ~ wave) for each student.
```{r}

```

##2. Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r}

```

#PART B: STAR WARS

##Install and load the {repurrrsive} package
```{r}
install.packages("repurrrsive")
library(repurrrsive)
```

##1. Use the sw_films list to identify how many characters were represented in each film
```{r}

```

##2 Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r}

```

#PART C: Some "basic" API calls
```{r}


```

