---
title: "Lab2_Akhila"
author: "Akhila"
date: "4/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
#install.packages("repurrrsive")
library(repurrrsive)
library(httr)

```

#PART A

##Run the code below to load the following data set.
```{r}

file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)

```

##Recode season to wave with the following code
```{r}

library(tidyverse)

benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))

```

##1. Fit a model of the form lm(math ~ wave) for each student.
```{r}
stu_split <- split(benchmarks, benchmarks$sid)
str(stu_split)


mods <- map(stu_split, ~lm(math ~ wave, data = .x))
str(mods)

```

##2. Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r}

#coef extracts coefficients for any model
coefs <- map(mods, ~coef(.x))
#OR map(mods, coef)

slopes <- map_dbl(coefs, ("wave"))
str(slopes)

relation <- tibble(student = names(slopes),
                   slope = slopes)

ggplot(relation, aes(slope)) +
  geom_histogram(fill = "forestgreen",
                 color = "white") +
  geom_vline(aes(xintercept = mean(slope, na.rm = TRUE)))

```

#PART B: STAR WARS

##Install and load the {repurrrsive} package
```{r}

# install.packages("repurrrsive")
library(repurrrsive)
```

##1. Use the sw_films list to identify how many characters were represented in each film
```{r}

length(sw_films)

chr_count <- map_dbl(sw_films, ~length(.x$characters))
chr_names <- map_chr(sw_films, "title")

tibble(Film = chr_names,
              Characters = chr_count)

```

##2 Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r}

str(sw_species)

hc <- map_chr(sw_species, "hair_colors")
str(hc)
species <- map_chr(sw_species, "name")
str(species)


tbl2 <- tibble(Species = species,
               `Hair Colors` = hc) %>% 
  filter(`Hair Colors` != "n/a" &
          `Hair Colors` != "none" & 
          `Hair Colors` != "unknown")

tbl2

```

#PART C: Some "basic" API calls
```{r}

ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
    content("parsed") 

str(ability1)
length(ability1$pokemon)

```

```{r}

abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
abs <- map(abilities, ~GET(.x) %>% 
                content("parsed"))

str(abs)
abs$pokemon

names <- map_chr(abs$pokemon, "name")
names

# tbl3 <- tibble(Pokemon = )
```


