---
title: "Lab2_Joanna"
author: "Joanna"
date: "4/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(httr)

```

#PART A

##Run the code below to load the following data set.
```{r}

file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)

```

##Recode season to wave with the following code
```{r}

library(tidyverse)

benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))

```

##1. Fit a model of the form lm(math ~ wave) for each student.
```{r}

# splitting by sid:
stu_split <- split(benchmarks, benchmarks$sid)
# str(stu_split)

# fit the model:
mods <- map(stu_split, ~lm(math ~ wave, data = .x))
# map: loops through each stu_split to fit lm(math ~ wave) for each
# str(mods)

```

##2. Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r}

#coef extracts coefficients for any model

coefs <- map(mods, ~coef(.x))
# what this does: 
# map(data, ~function(placeholder for each iteration))

# This would also work: 
# map(mods, coef)

# then extract the slopes:  
slopes <- map_dbl(coefs, ("wave"))
# return a dbl vector. loop through each list in coefs, extract "wave"
# str(slopes)

# to plot slopes, first create a tibble: 
relation <- tibble(student = names(slopes),
                   slope = slopes)

ggplot(relation, aes(slope)) +
  geom_histogram(fill = "forestgreen",
                 color = "white") +
  geom_vline(aes(xintercept = mean(slope, na.rm = TRUE)))

```

#PART B: STAR WARS

##Install and load the {repurrrsive} package
```{r}

# install.packages("repurrrsive")
library(repurrrsive)
```

##1. Use the sw_films list to identify how many characters were represented in each film


```{r}

length(sw_films)

chr_count <- map_dbl(sw_films, ~length(.x$characters))
chr_names <- map_chr(sw_films, "title")

tibble(Film = chr_names,
              Characters = chr_count)

# making tibble: 
# tibble(ColName = object)

```

##2 Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r}

# str(sw_species)

# loop to extract hair color and assign object
hc <- map_chr(sw_species, "hair_colors")
# str(hc)

# loop to extract species and assign object 
species <- map_chr(sw_species, "name")
# str(species)

# create tibble with both hair color and species name, filter out those with unknown hair color: 

tbl2 <- tibble(Species = species,
               `Hair Colors` = hc) %>% 
  filter(`Hair Colors` != "n/a" &
          `Hair Colors` != "none" & 
          `Hair Colors` != "unknown")

tbl2

```

#PART C: Some "basic" API calls
```{r}

ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
    content("parsed") 

# str(ability1)
length(ability1$pokemon)

ability1$name
length(ability1$pokemon)

```

##1 Use {purrr} to write an API call to obtain data on the first five abilities. Parse the JSON data to a list.

```{r}

abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
abs <- map(abilities, ~GET(.x) %>% 
                content("parsed"))

# str(abs)

```
##2 Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.

```{r}

ability_type <- map_chr(abs, "name")
number_of_pokemon <- map_dbl(abs, ~length(.x$pokemon))

tbl3 <- tibble(Ability = ability_type,
       `Number of Pokemon` = number_of_pokemon)

tbl3
```

##Bonus: Up to 1 point extra credit
Create a new data frame that lists the names of the pokemon with these specific abilities.
Hint: Try to get the name for one pokemon first, then extend out the logic to get all pokemon names. Also, this is really freaking hard so don’t spend too much time on it and don’t worry if you can’t figure it out.

```{r}


```


