---
title: "Rowley_lab2"
author: "Brock Rowley"
date: "4/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#install.packages("repurrrsive")
library(repurrrsive)
library(httr)
```
This lab will be similar to Lab 1 but will focus specifically on looping with {purrr}.

# Part A: Multiple Models
## Run the code below to load the following dataset.
```{r runthecode}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)
```

### These data represent individual student scores across seasonal benchmark screenings (administered in the fall, winter, and spring). The variables are as follows:
### **sid** = student identifier  
### **cohort** = student cohort  
### **sped** = special education status of the student for the given time point  
### **ethnicity** = coded race/ethnicity of the student  
### **frl** = free or reduced price lunch eligibility for the student for the given time point  
### **ell** = English language learner status for the student for the given time point  
### **season** = season the assessment was administered  
### **reading** = student’s reading score at the given time point  
### **math** = student’s mathematics score at the given time point  

## Recode season to wave with the following code
```{r recode_season}
benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))
benchmarks
```

## Fit a model of the form lm(math ~ wave) for each student.
```{r fit_lm}
stu_split <- split(benchmarks, benchmarks$sid)
str(stu_split)

mods <-map(stu_split, ~lm(math ~ wave, data = .x))
str(mods)
```

## Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r plot_slope_mean}
coefs <- map(mods, ~coef(.x))

slopes <- map_dbl(coefs, ("wave"))
relation <- tibble(student = names(slopes),
                   slope = slopes)
ggplot(relation, aes(slope))+
  geom_histogram(fill = "cornflowerblue",
                 color = "white") +
geom_vline(aes(xintercept = mean(slope, na.rm = TRUE)))

```

# Part B: Star Wars

## Use the sw_films list to identify how many characters were represented in each film.
```{r number_characters}
length(sw_films)
first_film <- sw_films[[1]]$characters
length(first_film)
chr_count <- map_dbl(sw_films, ~length(.x$characters))
film_name <- map_chr(sw_films, "title")

film_chr <- tibble( Film = film_name,
              Characters = chr_count)
film_chr
```


## Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r species_hair_colors}
str(sw_species)
hc <- map_chr(sw_species, "hair_colors")
str(hc)
species <- map_chr(sw_species, "name")
str(species)


tbl2 <- tibble(Species = species,
               `Hair Colors` = hc) %>% 
  filter(`Hair Colors` != "n/a" &
          `Hair Colors` != "none" & 
          `Hair Colors` != "unknown")

tbl2
```

# Part C: Some basic API calls
Many of the list elements have urls for API calls. 
For example = sw_films[[1]]$characters[1] will output:  
[1] "http://swapi.co/api/people/1/"
The above provides the url necessary to make an API call for all the information available on the first character in the first film. Unfortunately, this API has since been deprecated. However, we’re going to use essentially equivalent API calls to instead obtain data about pokemon, via https://pokeapi.co/. Feel free to visit the website and look around.

API’s are a way to host databases on the web, and make the data accessible via API calls. We’re going to look at abilities of pokemon. For example to obtain data on the first ability, we could run the following:
```{r abilites_pokemon}
ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
    content("parsed") 
```

The last digit in "https://pokeapi.co/api/v2/ability/1" is just an index denoting that this is the first ability listed in the database. To obtain data on the third ability, we would instead change our call to "https://pokeapi.co/api/v2/ability/3".

If you look at the parsed content (it comes in as JSON data) you will see it is a nested list, just like we worked with above for Star Wars.

We can identify what the specific ability is for ability 1 with: 
ability1$name will output:  
[1] "stench"
The number of pokemon with this ability with:
length(ability1$pokemon) will output:  
[1] 7

# Bonus: Up to 1 point extra credit
Create a new data frame that lists the names of the pokemon with these specific abilities.
```{r bonus_poke_names}
abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
abs <- map(abilities, ~GET(.x) %>% 
                content("parsed"))

str(abs)
abs$pokemon

names <- map_chr(abs$pokemon, "name")
names

tbl3 <- tibble(Pokemon = )
```

Hint: Try to get the name for one pokemon first, then extend out the logic to get all pokemon names. Also, this is really freaking hard so don’t spend too much time on it and don’t worry if you can’t figure it out.