---
title: "Stephanie lab2"
author: "Stephanie Gluck"
date: "4/13/2020"
output: html_document
---

```{r setup}
library(tidyverse)
#install.packages("repurrrsive")
library(repurrrsive)
library(httr)
```

This lab will be similar to Lab 1 but will focus specifically on looping with {purrr}.

# Part A: Multiple Models
## Run the code below to load the following dataset.
```{r runthecode}
file <- "https://github.com/datalorax/esvis/raw/master/data/benchmarks.rda"
load(url(file))
head(benchmarks)
```


## Recode season to wave with the following code
```{r recode_season}
benchmarks <- benchmarks %>%
    as_tibble() %>%
    mutate(wave = case_when(season == "Fall" ~ 0,
                            season == "Winter" ~ 1,
                            TRUE ~ 2))
benchmarks
```

## Fit a model of the form lm(math ~ wave) for each student.
```{r fit_lm}

stu_split <- split(benchmarks, benchmarks$sid)

mods <- map(stu_split, ~lm(math ~ wave, data = .x))
mods

```

## Plot the distribution of slopes. Annotate the plot with a vertical line for the mean.
```{r plot_slope_mean}

coefs <- map(mods, ~coef(.x))

#simplify version, since only one function 
#coefs <- map(mods, coef)

slopes <- map_dbl(coefs, "wave")
str(slopes)

relation <- tibble(student = names(slopes), 
                   slope = slopes)

ggplot(relation, aes(slope)) +
  geom_histogram(fill = "mediumorchid",
                 color = "white") +
  geom_vline(aes(xintercept = mean(slope, na.rm = TRUE)))

```

# Part B: Star Wars

## Use the sw_films list to identify how many characters were represented in each film.
```{r number_characters}

head(sw_films)
length(sw_films)

#for only the first film
sw_films[[1]]$characters
length(sw_films[[1]]$characters)

#using map 
chr_count <- map_dbl(sw_films, ~length(.x$characters))
chr_count

chr_names <- map_chr(sw_films, "title")
chr_names

tibble(Film = chr_names, 
              Characters = chr_count)

```


## Use the sw_species list to (a) identify species that have known hair colors and (b) identify what those hair colors are.
```{r species_hair_colors}

str(sw_species)

hc <- map_chr(sw_species, "hair_colors")
hc

species <- map_chr(sw_species, "name")
species

tbl2 <- tibble(Species = species, 
       `Hair Colors` = hc) %>% 
  filter(`Hair Colors` != "n/a" &
           `Hair Colors` != "none" & 
           `Hair Colors` != "unknown")
tbl2

```


# Part C: Some basic API calls

Pokemon example 

```{r abilites_pokemon}

library(httr)
ability1 <- GET("https://pokeapi.co/api/v2/ability/1") %>%
    content("parsed") 

attributes(ability1)
str(ability1)


#name of the ability 
ability1$name

#number of pokemon with this ability 
length(ability1$pokemon)

```


Use {purrr} to write an API call to obtain data on the first five abilities (note, we’re only using the first five to make the calls go fast, but the code would be essentially equivalent for any number of abilities you wanted to query). Make sure you parse the JSON data to a list.

### API call for first five abilities 

```{r, eval = FALSE}
abilities <- paste0("https://pokeapi.co/api/v2/ability/", 1:5)
abilities

abs <- map(abilities, ~GET(.x) %>% 
      content("parsed"))

abs

```


### Data frame of given ability and pokemon with that ability 

Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.

```{r}
#Use the parsed data to create a data frame that has the given ability, and the number of pokemon with that ability.

ability <- map_chr(abs, "name")

#extract length for 1 list
length(abs[[1]]$pokemon)

#convert into map 
count <- map(abs, list("pokemon")) %>% 
  map_dbl(~length(.x))

#create tibble 
tibble(Ability = str_to_title(ability), 
              `Number of Pokemon` = count)
```


# Bonus: Up to 1 point extra credit
Create a new data frame that lists the names of the pokemon with these specific abilities.
```{r bonus_poke_names}
#extract name of 1 pokemon
abs[[1]]$pokemon[[1]]$pokemon$name
abs[[1]]$pokemon[[2]]$pokemon$name

abs[[1]][["pokemon"]][[1]][["pokemon"]][["name"]]
abs[[1]][["pokemon"]][[2]][["pokemon"]][["name"]]

#individual level 
pokemon1 <- by_pokemon[[1]][1]
pokemon1[[1]]$pokemon$name
pokemon1[[1]][["pokemon"]][["name"]]

#extract pokemon list 
by_pokemon <- map(abs, "pokemon")
stench <- by_pokemon[1]

```

Hint: Try to get the name for one pokemon first, then extend out the logic to get all pokemon names. Also, this is really freaking hard so don’t spend too much time on it and don’t worry if you can’t figure it out.